---
title: "Create Validation Data"
author: "Annie Schmidt"
date: "8/24/2022"
output: html_document
---
## Overview
This .Rmd is set up to create a validation data set of labeled images for testing YOLO predictions.
It is intended to be run in multiple sessions to continue adding to the data set.
It requires a subset of images already randomly selected and placed in their own subdirectory in an aws s3 bucket.
It also requires an R script, validation_functions.R that has two essential functions.

## Getting set up
```{r setup, eval = TRUE, results = 'hide', message = FALSE, warning = FALSE}

library(tidyverse)
library(aws.s3)
# source functions you will be using
# set this path to wherever you save the r script (recommend just saving to desktop)
source("Z:/Informatics/S031/analyses/counting_penguins/scripts/validation_functions.R")

```

## Download images to tag
This function will check the pick list for available images, download the images, and update the picklist.
There is no undo so make sure you complete the images you download.
Running the function will also place a label key in the specified directory that can be used with makesense.ai
For current test parameters are as follows:
```{r run tile picker}

bucket = "s3://pb-adelie/"
prefix = "1920_UAV_survey/orthomosaics/croz/191202/croz_20191202_tiles/"
tile_list = "croz_20191202_validation_tile_list.csv"

# Run tile picker function including your initials and the location on your local machine where you want to download images to
# this directory will get cleared to best to make a fresh one on your desktop for this purpose
# n = the number of images it will down load. Recommend doing small chunks of 3-5 so you can ensure you complete them all
tile_picker(
 tile_list = tile_list,
 bucket = bucket,
 prefix = prefix,
 initials = "AS",
 wd = "C:/Users/aschmidt/Desktop/test_images/",
 n = 5)

# now you can upload the images to makesense.ai to tag

```

## Upload label data and combine with existing data
Run update_labs function to update label data in s3
Will need to move label.zip file from downloads to working directory first

```{r run label updater}
update_labs(
  bucket,
  prefix,
  tile_list)

```